\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-19 tex/paper.tex
save

    \item $\smash{\hat\theta}_f$ maximimizes the entropy
    $H(p_{Z|f(X;\theta_f)})$, which happens when all outcomes of
    $Z|f(X;\smash{\hat\theta}_f)$ are equally likely and in which case
    $p(z|f(X;\smash{\hat\theta}_f)) = p(z)$ for all $z \in {\cal Z}$ since we
    require a uniform prior by construction. Note that in the continuous case,
    the supremum of the differential entropy over continuous distributions on
    the same bounded support is also realized by the uniform distribution over
    that support.
\end{itemize}
When the lower bound is active, we have $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$
because of the second condition, and because of Proposition~\ref{prop:1}, the
optimal classifier $f(\cdot;\smash{\hat\theta}_f)$ is therefore also a pivotal
quantity.

>>>>

    \item $\smash{\hat\theta}_f$ maximimizes the entropy
    $H(p_{Z|f(X;\theta_f)})$, which happens when all outcomes of
    $Z|f(X;\smash{\hat\theta}_f)$ are equally likely and in which case
    $p(z|f(X;\smash{\hat\theta}_f)) = p(z)$ for all $z \in {\cal Z}$ since we
    require a uniform prior by construction. Note that in the continuous case,
    the supremum of the differential entropy over continuous distributions on
    the same bounded support is also realized by the uniform distribution over
    that support.
\end{itemize}
When the lower bound is active, we have $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$
because of the second condition, which induces that the
optimal classifier $f(\cdot;\smash{\hat\theta}_f)$ is also a pivotal
quantity as a consequence of Proposition~\ref{prop:1}.
